\textit{Supporting Information for}: How is experience transformed into memory?

### 2019-08-30 paper/supporting_information.tex
added k_optimization fig to supporting information

%\begin{figure}[p!]
%\centering
%\includegraphics[width=\textwidth]{figs/k_optimization}
%\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}. This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
%\label{fig:k_optimization}
%\end{figure}

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/k_optimization}
\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}. This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
\label{fig:k_optimization}
\end{figure}
